---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# easyenrich

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/easyenrich)](https://CRAN.R-project.org/package=easyenrich)
<!-- badges: end -->

Test whether counts of an element differs between 2 groups. For example identify which genes are present at different rates in lists of 'mutated genes' from two different cohorts. **easyenrich** creates 1 contingency table for every element in a list of vectors, summarising counts of their presence/absence in each cohort (represented as the different vectors in the list). It also runs the fisher test, applies MTC, and produces forest plots to visualise the results.


## Installation

You can install the development version of easyenrich like so:

``` r
if (!require("remotes"))
    install.packages("remotes")

remotes::install_github("CCICB/easyenrich")
```

## Quick Start


```{r example}
library(easyenrich)

#Step 1: Create a list of two or more vectors.  
input <- list(
 colorectal = c("APC", "APC", "APC", "TP53", "APC"),
 melanoma = c("BRAF", "BRAF", "BRAF", "BRAF", "BRAF", "TP53", "APC")
)

# Step 2: Create contingency tables
contingency_tables <- list_to_contingency_tables(input)

# Step 3: Compute fisher p values & odds ratios
comparison <- contingency_tables_to_fisher(contingency_tables)

# Step 4: Sort results based on fdr
comparison[order(comparison$fdr),]

# Step 5: Visualise Results
plot_rainforest(comparison)
```
